ggalluvial: Layered Grammar for Alluvial Plots

### 2020-03-04 README.rmd
link to contributing guidelines & code of conduct from readme

[Issues](https://github.com/corybrunson/ggalluvial/issues) and [pull requests](https://github.com/corybrunson/ggalluvial/pulls) are more than welcome! Pretty much every fix and feature of this package derives from a problem or question posed by someone with datasets or design goals i hadn't anticipated.

>>>>

Contributions in any form are more than welcome! Pretty much every fix and feature of this package derives from a problem or question posed by someone with datasets or design goals i hadn't anticipated. See the [CONTRIBUTING](CONTRIBUTING.md) file for guidance, and please respect the [Code of Conduct](CODE_OF_CONDUCT.md).
